Delone lattice studies in \CIII, the space of three complex variables

### 2022-12-22 C3/C3.tex
Just messing with the table
just formatting of the .tex file

	The scalars used by \citeasnoun{Delaunay1932} in his formulation of Selling reduction \cite{Selling1874}
	are (in the conventional order) $b \cdot c$, $a \cdot c$, $a \cdot b$, $a \cdot d$, 
	$b \cdot d$, $c \cdot d$, where $d = -a-b-c$. 
	(As a mnemonic device, 
	observe that the first three terms use
	$\alpha$, $\beta$, and $\gamma$, 
	in that order, 
	and the following terms use $a$, $b$, $c$, in that order.)

	\citeasnoun{andrews2019b} chose to 
	represent the scalars in the space \SVI{},
	\Svec{} (defined in the order above), 
	as a way to create a metric space
	for the measurement of the distance between lattices. T
	hey also consider the representation of this space as the
	space of three complex dimensions, \CIII{} or 
	{$\{c_1$}, {$c_2$}, {$c_3\}$}.

	In \CIII{}, in terms of the Delone scalars, 
	a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of \citeasnoun{Delaunay1932} (see \citeasnoun{andrews2019a}).
	As a memonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).

		\citeasnoun{andrews2019b} considered the matrix representations of the reflections in \CIII{} (and in \SVI{}). 
		This paper will describe the boundary transformations 
		at the edges of the fundamental	unit of \CIII{}. 
		In \SVI{}, the fundamental unit is the all negative orthant, 
		which contains only and	all of the reduced cells. 
		In \SVI{} and \CIII{}, 
		the boundaries are found where any scalar 
		(or correspondingly the real or imaginary part) 
		is equal to zero. The rationale for this work was 
		that it might lend insights into the topology of
		 the space of lattices.

@@

	Next we define the operators in \CIII{} t
	hat will be used in the matrix descriptions of 
	the transformations at the boundaries of the fundamental unit.\\
	See Table \ref{tab:operators}.

\begin{table}	
	\label{tab:operators}
	\begin{tabular}{c l l l }
\toprule
	Operator
						&Usage	
													&Result	
																			&Name\\
\midrule
	$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
	$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
	$\textfrak{P}_r$ 	& $ \textfrak{P}_r(c_j)$ 	& $(x_j, x_j)$ 			& Plus real\\ 
	$\textfrak{P}_i$ 	&  $\textfrak{P}_i(c_j)$  	& $(y_j, y_j)$ 			& Plus imag\\ 
	$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ 				& Real \\ 
	$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ 				& Imaginary\\

\bottomrule
	\end{tabular}		
\end{table}

@@

\citeasnoun{Delaunay1932} does not consider the boundary transformations 
in detail. However, he uses them to define the process of Selling reduction. 
For example in \SVI{}, he lists the following as one of the possible results 
for a transformation on \si{}.
\SvecA{}
The third matrix above (the third boundary transform for $s_1$) implements this operation and interchanges the
real part of \ciii{} and the imaginary part of \cii{}.

@@

In terms of \CIII, Delone's alternate transformation for the \si{} boundary would
exchange the real of \cii{} with the imaginary part of \ciii{}. That is the fourth
matrix in the list for \si{}. The other two transformations for \si{} can 
be generated from the two we have just displayed by the "exchange operation" \cite{andrews2019b} applied to the second and third \CIII{} elements. Delone 
did not describe the latter two transformation, perhaps because even a
single transformation was adequate to implement reduction. He already listed
two.

@@

The considerable regularity of the transformation matrices (above) highlights one
of the important aspects of Selling reduction as used by \citeasnoun{Delaunay1932}
when compared to Niggli reduction \cite{Niggli1928}. Where all the 
boundaries of the fundamental orthant in \CIII ~and \SVI{} are basically the same (and indeed are 
related by reflections), the boundaries formed in Niggli reduction
are of multiple types, and the fundamental unit of the space
representing Niggli reduced cells (\GVI{}, see \citeasnoun{Andrews2014}) is non-convex.

@@

Several aspects of C3 are obvious from inspecting the matrices above. 
First, we see that each boundary has four possible 
transformations that
can be applied. Because the each of the transformations at boundaries are 
self-inverse, they are the same transformations that would 
be used in the process of cell (lattice) reduction. 
\citeasnoun{Delaunay1932} and  \citeasnoun{Delone1975} give 
only two choices. Presumably for simplicity they did not list
the transformations that used the "exchange" operator 
(see \cite{andrews2019b}).

>>>>

	The scalars used by~\citeasnoun{Delaunay1932} in his formulation of Selling reduction ~\cite{Selling1874}
	are (in the conventional order) $b \cdot c$, $a \cdot c$, $a \cdot b$, $a \cdot d$, 
	$b \cdot d$, $c \cdot d$, where $d = -a-b-c$. 
	(As a mnemonic device, 
	observe that the first three terms use
	$\alpha$, $\beta$, and $\gamma$, 
	in that order, 
	and the following terms use $a$, $b$, $c$, in that order.)

	~\citeasnoun{andrews2019b} chose to 
	represent the scalars in the space \SVI{},
	\Svec{} (defined in the order above), 
	as a way to create a metric space
	for the measurement of the distance between lattices. T
	hey also consider the representation of this space as the
	space of three complex dimensions, \CIII{} or 
	{$\{c_1$}, {$c_2$}, {$c_3\}$}.

	In \CIII{}, in terms of the Delone scalars, 
	a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932} (see~\citeasnoun{andrews2019a}).
	As a memonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).

	~\citeasnoun{andrews2019b} considered the matrix representations 
	of the reflections in \CIII{} (and in \SVI{}). 
	This paper will describe the boundary transformations 
	at the edges of the fundamental	unit of \CIII{}. 
	In \SVI{}, the fundamental unit is the all negative orthant, 
	which contains only and	all of the reduced cells. 
	In \SVI{} and \CIII{}, 
	the boundaries are found where any scalar 
	(or correspondingly the real or imaginary part) 
	is equal to zero. The rationale for this work was 
	that it might lend insights into the topology of
	the space of lattices.

@@

	Next we define the operators in \CIII{} t
	hat will be used in the matrix descriptions of 
	the transformations at the boundaries of the fundamental unit.\\
	See Table ~\ref{tab:operators}.

	\begin{table}	
		\label{tab:operators}
		\begin{tabular}{c l l l }
			\toprule
			Operator			&Usage						&Result					&Name\\
			\midrule
			$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
			$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
			$\textfrak{P}_r$ 	& $ \textfrak{P}_r(c_j)$ 	& $(x_j, x_j)$ 			& Plus real\\ 
			$\textfrak{P}_i$ 	&  $\textfrak{P}_i(c_j)$  	& $(y_j, y_j)$ 			& Plus imag\\ 
			$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ 				& Real \\ 
			$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ 				& Imaginary\\
			\bottomrule
		\end{tabular}		
	\end{table}

@@

	~\citeasnoun{Delaunay1932} does not 
	consider the boundary transformations 
	in detail. 
	However, he uses them to 
	define the process of Selling reduction. 
	For example in \SVI{}, 
	he lists the following as one of the possible results 
	for a transformation on \si{}:
	\SvecA{}.
	The third matrix above 
	(the third boundary transform for $s_1$) 
	implements this operation and interchanges the
	real part of \ciii{} and the imaginary part of \cii{}.

@@

	If considered in \CIII, Delone's alternate transformation 
	for the \si{} boundary would
	exchange the real of \cii{} 
	with the imaginary part of \ciii{}. That is the fourth
	matrix in the list for \si{}. 
	The other two transformations for \si{} can 
	be generated from the two we have 
	just displayed by the "exchange operation"~\cite{andrews2019b} 
	applied to the second and third \CIII{} elements. Delone 
	did not describe the latter two transformation, 
	perhaps because even a single transformation 
	was adequate to implement reduction. He already listed two.

@@

	The considerable regularity 
	of the transformation matrices (above) highlights one
	of the important aspects of Selling reduction 
	as used by~\citeasnoun{Delaunay1932}
	when compared to Niggli reduction~\cite{Niggli1928}. 
	Where all the 	boundaries of the fundamental orthant 
	in \CIII ~and \SVI{} are basically the same 
	(and indeed are related by reflections), 
	the boundaries formed in Niggli reduction are of multiple types, 
	and the fundamental unit of the space representing 
	Niggli reduced cells (\GVI{}, see~\citeasnoun{Andrews2014}) is non-convex.

@@

	Several aspects of C3 are obvious from inspecting the matrices above. 
	First, we see that each boundary has four possible 
	transformations that can be applied. 
	Because the each of the transformations at boundaries are self-inverse, 
	they are the same transformations that would 
	be used in the process of cell (lattice) reduction. 
	~\citeasnoun{Delaunay1932} and~\citeasnoun{Delone1975} give 
	only two choices. Presumably for simplicity they did not list
	the transformations that used the "exchange" operator 
	(see~\cite{andrews2019b}).
